Heavy inextensible strings in the Schwarzschild geometry

### 2024-11-01 weighted_string.Rmd
longer integration
tighter limits

dist <- 1.04
lambda <- seq(from = 0, to = -1, by = -0.1)

f <- approxfun(
    c(0,-0.1,-0.2,-0.5, -0.7, -1,  -1.4,     -1.6,-1.7),
    c(2.4,2.4, 2.1,1.5,   1.5, 0.9,  0.63, 0.3,0)
)

@@

segments(dist,0,4,0)
docolour <- function(lambda,...){
    points(string(r0 = dist, lambda = lambda, angles=seq(0,f(lambda),0.01)), type='l', lwd=3, ...)
}
docolour(0,col='red')
docolour(-1,col='blue')
points(dist,0,pch=16)
```

>>>>

dist <- 1.04
lambda <- seq(from = 0, to = -1.15, by = -0.1)

f <- approxfun(
    c(0,-0.1,-0.2,-0.5, -0.7, -1,  -1.15, -1.1, -1.4,     -1.6,-1.7),
    c(3.4,2.9, 2.7,1.9,   1.5, 0.9,  0.4,  0.6,   0.63,    0.3    ,0)
    )

@@

segments(dist,0,4,0)
docolour <- function(lambda,...){
    points(string(r0 = dist, lambda = lambda, angles=seq(0,f(lambda),0.01)), type='l', lwd=3, ...)
}
docolour(0,col='red')
docolour(-1,col='blue')
docolour(-1.15,col='green')
points(dist,0,pch=16)
```
